Acceleration of Derivative Calculations with Application to Radial Basis Function ­ Finite-Differences on the Intel MIC Architecture

### 2014-06-10 slides/2014_ics/slides-ics.tex
ccl

\begin{frame}
  \frame{Conclusion}

  \begin{block}{Conclusion}
  \end{block}

>>>>

\begin{frame}
  \frametitle{Conclusion}

  \begin{block}{Conclusion}
    \begin{itemize}
    \item RBF-FD needs to compute different derivative of multiple functions.
    \item The different derivatives have the same sparsity structure.
    \item Idea: perform all the derivatives simultaneously
    \item The flop-to-byte ratio increases significantly
    \item Vector reordering operations of Xeon Phi enables efficient execution
    \item Performs efficiently: 
      \begin{itemize}
      \item 3.5 times faster than peak of traditional SpMV  
      \item faster than peak of SpMM (v=4)
      \end{itemize}
    \end{itemize}
  \end{block}
